Synthesizing by means of mice

### 2020-08-09 mice_synthesizing/Mice_Synthesizing.Rmd
Adjusted degrees of freedom - one new night of running simulations.

It can be seen that the bias indeed decreases, while the standard error of the estimates increases. This is due to the fact that the within-imputation variance increases, while the between-imputation variance decreases somewhat. When we use the same approach to estimate the bootstrapped boys data, we get the following results.

@@

@@

cart_adj <- boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), 
            Between = mean(bm), 
            Total = mean(var),
            .groups = 'drop')

bind_rows("Cart default" = cart_default,
          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

>>>>

Additionally, the same approach is used to synthesize the `r nsim` bootstrapped samples from the completed boys data.

@@

However, I'm not sure whether it is sensible to set the number of iterations to `maxit = 1`. Therefore, I additionally included an example that shows the same approach, that is, with the complexity parameter `cp = 1e-08` and the parameter `minbucket = 3`, but with maximum number of iterations fixed at `maxit = 5`.

```{r}
boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

It can be seen that the bias indeed decreases, while the standard error of the estimates increases. This is due to the fact that the within-imputation variance increases, while the between-imputation variance decreases somewhat.

@@

cart_adj_maxit <- boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), 
            Between = mean(bm), 
            Total = mean(var),
            .groups = 'drop')

cart_adj <- boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool.syn) %>%
  group_by(term) %>%
  summarise(Within = mean(ubar), 
            Between = mean(bm), 
            Total = mean(var),
            .groups = 'drop')

bind_rows("Cart default" = cart_default,
          "Cart with adjusted settings and maxit = 1" = cart_adj_maxit,
          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# Adjusted degrees of freedom

Next to the analyses displayed previously, I adjusted the degrees of freedom to $\text{max}(m - 1, \nu)$, as is done in Reiter and Drechsler (2010). This yields the following results for the initial analyses, that is, bootstrapping with the mice default settings, but with the method set to `cart`. Note that this concerns `r nsim` bootstrap samples from the complete data.

```{r}
boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool2.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

Additionally, the results can be computed for the data with the smaller bias settings. That is, setting `maxit = 1`, `cp = 1e-08` and `minbucket = 3`.

```{r}
boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool2.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

And, once again, the same analysis as the previous one, but with `maxit = 5`.

```{r}
boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool2.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
